\documentclass[line, margin]{res}
\newcommand{\CS}{C\nolinebreak\hspace{-.05em}\raisebox{.6ex}{\scriptsize\bf \#}}
\newcommand{\ts}{\textsuperscript}
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	urlcolor=blue
}
\addtolength{\topmargin}{-.375in}
\addtolength{\footskip}{-.5in}
\addtolength{\textheight}{1in}

\begin{document}
\name{H. Chase Stevens}
\address{24 Lutton Place, Edinburgh, Scotland EH8 9PE | 001 44 7719 663016 | chase@chasestevens.com}

\begin{resume}
\section{EDUCATION}
\textbf{University of Edinburgh}, Edinburgh, UK \hfill 2011-Present\\
Master of Arts Honors Cognitive Science \\
Expected to graduate May 2015 \\[5pt]
\textbf{University of Southern Maine}, Portland, ME, USA \hfill 2009-2011\\
Non-degree candidate\\[5pt]
\textbf{The New School}, Kennebunk, ME, USA \hfill 2007-2010\\
Senior Project: Taught semester-long course in Python \\
Graduated Valedictorian

\section{TECHNICAL SKILLS}
\begin{itemize}[leftmargin=10pt]
\item Programming Languages: Python, PHP, Java, \CS, Javascript
\item Markup: HTML4/5, CSS3
\item Data: MySQL, Microsoft SQL Server
\item IDEs: Visual Studio, Eclipse
\item VCSs: Git, SVN
\end{itemize}

\section{POSITIONS HELD}
\textit{Undergraduate Software Engineer at Skyscanner, Ltd.} \hfill August 2013 - Present \\
Duties include development and maintenance of web scrapers as part of Data Acquisition and Reporting team, prototyping and implementation of experimental projects as part of Research and Development division. Edinburgh, UK.\\[5pt]
\textit{Intern, Data Acquisition at Skyscanner, Ltd.} \hfill May 2013 - August 2013 \\
Duties included writing, maintaining, and ensuring the accuracy of web scrapers, collaborating with technical and non-technical staff, liaising with commercial partners and other 3rd parties. Edinburgh, UK.\\[5pt]
\textit{Quality Assurance Engineer Intern at CashStar, Inc.} \hfill June 2011 - August 2011 \\
Duties included ensuring client specification adherence, development of data management and entry system. Portland, ME, USA.\\[5pt]
\textit{Intern at Law Offices of Nichols, Webb \& Loranger} \hfill 2007 - 2011 \\
Duties included analysis and summary of legal documents, discovery, and scientific publications, as well as web development and various information technology tasks. Saco, ME, USA.

\section{VOLUNTEER EXPERIENCE}
\textit{Web Design and Development for Chase-Jellison Homestead} \hfill 2012 - Present \\
Duties include ongoing design and development of desktop and mobile websites, as well as database management. \\[5pt]
\textit{Member of Board of Directors of The New School Corporation} \hfill 2009 - 2011 \\
Entailed responsibility for ensuring 501(c)(3) corporation complied with by-laws and mission statement. Duties included analysis and ratification of policies for The New School (Kennebunk, ME, USA) as well as approval of budgetary proposals for same. 

\section{SELECTED HONORS AND AWARDS}
\begin{tabular}{@{}l l}
May 2013 & \textit{J.P. Morgan Spring Week in Technology Coding Challenge 3\ts{rd} Place}\linebreak \\[5pt]
February 2013 & \textit{\href{http://data.inf.ed.ac.uk/ilwhack/finalprojects.php}{University of Edinburgh Smart Data Hack} ``Community App Award''}\linebreak\\[1pt] 
&\textit{for \href{https://github.com/team-tusive/ilwhack}{SaferRoute} (Team Leader)} \linebreak \\[5pt]
May 2012 & \textit{\href{https://sites.google.com/site/2012oop/winners}{University of Edinburgh INF1-OP} ``Best Project (Experienced)'' for} \linebreak \\[1pt] 
 &\textit{\href{http://www.chasestevens.com/team2civ/}{StratLoc}} \linebreak \\[5pt]
Spring 2010 & \textit{National Merit Scholar Finalist (highest rank)} \\[5pt]
Spring 2010 & \textit{Valedictorian of The New School Class of 2010} \\[5pt]
Spring 2010 & \textit{The New School Teacher of the Year} \\[5pt]
\end{tabular}
\end{resume}
\end{document}
